Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-13 tex/nusselt_paper.tex
Adding refs to Lecoanet (check MNRAS formatting for PRL) in IMEX section.

@@

The atmosphere is contained between two impenetrable, stress free, fixed temperature boundaries at
the top and bottom of the domain such that $w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
is periodic in the horizontal. We utilize the novel Dedalus\footnote{http://dedalus-project.org/} pseudospectral framework 
 to time-evolve Eqs. 
\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit third-order four-step 
Runge-Kutta timestepping scheme \cite{ascher&all1997}.  
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  Our physical grid sizes range from
96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
By using IMEX timestepping, we can implicitly step the stiff linear acoustic wave contribution and we are able to
efficiently study flows at moderate ($Ma \approx 1$) and very low ($Ma \approx 10^{-4}$)
Mach number (Fig. \ref{fig:ma_v_eps}b).

>>>>

\newcommand\mnras{{MNRAS}}%
          % Monthly Notices of the RAS

@@

The atmosphere is contained between two impenetrable, stress free, fixed temperature boundaries at
the top and bottom of the domain such that $w = \partial_z u = T_1 = 0$ at $z = \{0, L_z\}$. The domain
is periodic in the horizontal. We utilize the novel Dedalus\footnote{http://dedalus-project.org/} pseudospectral framework 
 to time-evolve Eqs. 
\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using an implicit-explicit third-order four-step 
Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  Our physical grid sizes range from
96x384 grid points at the lowest values of Ra to 1152x4608 grid points at Ra $\geq 10^{7}$. 
By using IMEX timestepping, we implicitly step the stiff linear acoustic wave contribution and we are able to
efficiently study flows at moderate ($Ma \approx 1$) and very low ($Ma \approx 10^{-4}$)
Mach number (Fig. \ref{fig:ma_v_eps}b).  Our equations take the form
of the FC equations in \cite{lecoanet&all2014}, extended to include variable
$\nu$ and $\chi$, and we follow the approach there; this IMEX approach has been successfully 
tested against a nonlinear benchmark  of the compressible Kelvin-Helmholtz instability \cite{Lecoanet_et_al_2016_KH}.
